ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Clarify where to specify common-properties

Frequently, experimental series hold certain properties constant, such as initial
mixture composition or pressure, and use the same method to detect ignition delay.
\ck{} files support a \yabox|common-properties| convenience section where these
common details may be defined once, and referenced in each datapoint.
This block uses the ability of YAML files to define an anchor with the
\yabox|&| symbol and refer to that section later with the \yabox|*| symbol:
%
\begin{yamlbox}
common-properties:
  composition: &comp
    kind: mole fraction
    species:
      ...
  ignition-type: &ign
    ...
datapoints:
  composition: *comp
  ignition-type: *ign
  temperature: 1000 kelvin
  ...
\end{yamlbox}
%
The \yabox|common-properties| section is not required, but can save space and
help avoid errors when several data points share some common values. However, even if
properties are specified in the \yabox|common-properties| section, they must also be
explicitly specified and referenced in the \yabox|datapoints| section for each data point,
as seen in the previous code.

>>>>

Frequently, experimental series hold certain properties constant, such as initial mixture
composition or pressure, and use the same method to detect ignition delay. \ck{} files support a
\yabox|common-properties| convenience section where these common details may be defined once, and
referenced in each element of the \yabox|datapoints| sequence. This block uses the ability of YAML
files to define an anchor with the \yabox|&| symbol and refer to that section later with the
\yabox|*| symbol:
%
\begin{yamlbox}
common-properties:
  composition: &comp
    kind: mole fraction
    species:
      ...
  ignition-type: &ign
    ...
datapoints:
  composition: *comp
  ignition-type: *ign
  temperature: 1000 kelvin
  ...
\end{yamlbox}
%
The \yabox|common-properties| section is not required, but can save space and
help avoid errors when several data points share some common values. However, even if
properties are specified in the \yabox|common-properties| section, they must also be
explicitly specified and referenced in the \yabox|datapoints| section for each data point,
as seen in the previous code.
